### 2012-12-07 doc/description.tex
uodates in description;

\subsection{Mapping of Types}
The mapping of types assumes a bijection between application types and database types, otherwise these has to be additional information for type mapping. We focus on structural and data change therefore we simplify types and its mapping.
\begin{verbatim}
op type2type : App-Type -> Db-Type .
eq type2type(APP-STRING) = DB-STRING .
\end{verbatim}

@@

\begin{verbatim}
op class2table : Class -> Table .
eq class2table(C) = table(name(C), primaryKey('Id), 
                    props2cols(singlePropertyList(C)), []) .
\end{verbatim}

@@

\subsubsection{Mapping of Single Properties}
\begin{verbatim}
op props2cols : List{Property} -> List{Column} .
	eq props2cols([]) = ([]).List{Column} .
	eq props2cols(Props) = prop2col(head(Props)) props2cols(tail(Props)) .
\end{verbatim}

>>>>

\subsection{Mapping of Types}
The mapping of types assumes a bijection between application types and database types, otherwise these has to be additional information for type mapping. We focus on structural and data change therefore we simplify types and its mapping.
\begin{verbatim}
op type2type : App-Type -> Db-Type .

eq type2type(APP-STRING) = DB-STRING .
\end{verbatim}

@@

\begin{verbatim}
op class2table : Class -> Table .

eq class2table(C) = table(name(C), primaryKey('Id), 
                    props2cols(singlePropertyList(C)), []) .
\end{verbatim}

@@

\subsubsection{Mapping of Single Property}
Each single property is mapped to a column, when the cardinality is equal to 1 the NOTNULL constraint is added to a column. 
\begin{verbatim}
op props2cols : List{Property} -> List{Column} .
op props2cols : Property -> Column .

eq props2cols([]) = ([]).List{Column} .
ceq props2cols(Prop) = [] if cardinality(Prop) > 2 .
ceq props2cols(Prop) = column(name(Prop), type2type(type(Prop)), NOTNULL)
    if cardinality(Prop) == 1 .
ceq props2cols(Prop) = column(name(Prop), type2type(type(Prop)), []) 
   if cardinality(Prop) == 0 .
eq props2cols(Props) = props2cols(head(Props)) props2cols(tail(Props)) .
\end{verbatim}
A property with cardinality greater than one has to be mapped int a table not a column, thus we have a special mapping function for collections.

\subsubsection{Mapping of Collections}
A property collection is mapped into a table which contains a foreign key. The key references the table representing the owning class.
\begin{verbatim}
op collections2tables : Qid List{Property} -> List{Table} .
op collections2tables : Qid Property -> Table .

eq collections2tables(Q, []) = ([]).List{Table} .
eq collections2tables(Q, Prop) = table(name(Prop), primaryKey('Id), 
   column('value, type2type(type(Prop)), [] ), foreignKey(Q, Q, NOTNULL)) .
eq collections2tables(Q, Props) = collections2tables(Q, head(Props)) 
   collections2tables(Q, tail(Props)) .
\end{verbatim}

\subsection{Mapping of Associations}
\begin{verbatim}

\end{verbatim}
